conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-07-16 paper/paper.Rmd
Updated abstract

[comment]: Revised, edited text below the original text.

@@

A higher level of granularity however is sometimes required to make public health decisions for a given population.

[ What's different and useful about conmat? ]

>>>>

@@

[ What's different and useful about conmat? ] 
A higher level of granularity however is sometimes required to make public health decisions for a given population.

`conmat` also provides flexibility, in that it allows users to specify the area in which they would like the contact matrices to be generated; it allows users to specify their own age groups and population structures; it allows users to upload their own contact surveys to fit the model on; and it allows users to generate the contact matrices at different settings.
